The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-12 thesis/paper.tex
stuff

\subsection{API Design} \label{api_design}
API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}. Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}. More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}. When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}. One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing} \cite{shi2011empirical}. The design decisions reached during development of an API will affect the overall usability of the API. Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.

@@

%%Lehman's laws (!!!improve later)
Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}. The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}. The laws are said to only apply to E-type systems, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.

@@

\subsection{API Evolution} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.

@@

%%Possibly add a paragraph here to

@@

%The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study.

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.

@@

The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.

@@

\smallskip \noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short period of its lifetime. It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider these factors to be the remaining threats to construct validity.

@@

\smallskip \noindent
\textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}. In addition to that, strategies from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} \cite{robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis. The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study. The semi-structured nature of the interview, might threaten the reproducibility; however, large parts of it were structured around existing theories.

>>>>

\subsection{API Design} \label{api_design}
API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.

 Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}. More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}. When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}. One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing, shi2011empirical}. The design decisions reached during development of an API will affect the overall usability of the API. Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.

@@

%%Lehman's laws (!!!improve later)
Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}. The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.

@@

\subsection{API Evolution} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring, shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.

@@

%%Possibly add a paragraph here to motivate the gap more

@@

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.

@@

The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines, seaman1999qualitative}.

@@

\smallskip \noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short period of its lifetime. It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider these factors to be the remaining threats to construct validity.

@@

\smallskip \noindent
\textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}. In addition to that, strategies from additional well-established papers \cite{andersson2007spiral, seaman1999qualitative, robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis. The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study. The semi-structured nature of the interview, might threaten the reproducibility; however, large parts of it were structured around existing theories.
